Robust Fault-Tolerant Control and Motion Planning of UAVs and Biped Robots Team System for S\&R Usage

### 2022-09-22 paper/paper.tex
move folder oneRobot to src/UTRSmainScript/Robot, add content in simulation in paper.tex, adjust the format of fig in rb.EXE_PLOT in oneRobot_FaFs.m

\documentclass{ieeeaccess}
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{mathtools}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{float}
\usepackage[flushleft]{threeparttable}
\usepackage{bm}
\usepackage[inline]{enumitem} 
% \usepackage{amsmath}
% \usepackage{amsfonts}
% \usepackage{amssymb}
% \usepackage{fontspec}
% \setmainfont{TeX Gyre Termes}
\setcounter{MaxMatrixCols}{30}
\providecommand{\U}[1]{\protect\rule{.1in}{.1in}}
\newtheorem{theorem}{Theorem}
\newtheorem{acknowledgement}[theorem]{Acknowledgement}
\newtheorem{algorithm}[theorem]{Algorithm}
% \newtheorem{axiom}[theorem]{Axiom}
\newtheorem{case}[theorem]{Case}
% \newtheorem{claim}[theorem]{Claim}
\newtheorem{conclusion}[theorem]{Conclusion}
% \newtheorem{condition}[theorem]{Condition}
% \newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{corollary}[theorem]{Corollary}
% \newtheorem{criterion}[theorem]{Criterion}
\newtheorem{definition}[theorem]{Definition}
% \newtheorem{example}[theorem]{Example}
% \newtheorem{exercise}[theorem]{Exercise}
\newtheorem{lemma}{Lemma}
\newtheorem{notation}{Notation}
\newtheorem{problem}[theorem]{Problem}
% \newtheorem{proposition}[theorem]{Proposition}
\newtheorem{remark}{Remark}
\newtheorem{solution}[theorem]{Solution}
% \newtheorem{summary}[theorem]{Summary}
\newtheorem{assumption}{Assumption}[section]
\newtheorem{ramark}{Remark}[section]
\newenvironment{proof}[1][Proof]{\noindent\textbf{#1.} }{\ \rule{0.5em}{0.5em}}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

@@

\subsection{Task Allocation}
In the URTS, it can be expected that each agent will be assigned several specific tasks, such as searching a specific area, or delivering supplies to disaster area, etc. However, the number of agents and tasks is more than one, and each agent has different capabilities (e.g. moving speed or load capacity) and status (e.g. their own position or the amount of supplies carried), and each task has different characteristics (e.g. Urgency, position, amout of supplies needed). Therefore, the results of task allocation can be "good or bad", which leads us want to find the optimal allocation. This problem is refered as a task allocation problem or multi-robot task allocation problem. A problem formulation and a mathematical model of problem can be found in \cite{Khamis2015}. Although there are many different formulations and models to solve the task allocation problem, the common goal is to find a set of task-agent pairs to achieve a specific cost function. In this paper, we assume that the tasks have been properly assigned and therefore do not further discuss this issue. In other words, every agent knows a destinition $q_{goal}$ it needs to go at every moment.
% $(\mathcal{G})_n, n\in\mathbb{Z}\cap[1, N], N\in\mathbb{Z}^+$
\textit{
    \begin{remark}
        This block is like a commander since it is used to assign task for agents. Thus, if the real S\&R system has human experts as commanders, he can replace its job or make decisions together with it to maximize the rescue value.
    \end{remark}
}

\subsection{Path Planning}
After a target point is assigned for each agent, next step is to find a collision-free path from current position to it. There must exist multiple feasible paths to go. Similar to task allocation, we usually want to find an optimal path. There are several path planning algorithm to handle this problem. Due to the developmental and universal nature of roadmap-based path planning algorithm, this paper uses it as the path planning method of UTRS. This method attempts to discretize the search space into interconnected roads and find the path on it. 
% According to the roadmap construction method, it can be divided into deterministic and sample-based.

@@

By treating a roadmap-based path planning algorithm as a black box, the output is a sequence (or sayed waypoints), and the three inputs are current configuration $q_{start}$, goal configuration $q_{goal}$, and configuration space $\mathcal{C}$. Current configuration is obtained by GPS, inertial measurement unit, or other locating techniques. Goal configuration is obtained by the previous block, Task Allocation. Configuration space $\mathcal{C}$ is constructed by environment information through sensors of agents online or in advance by human knowledge offline. $\mathcal{C}$ is a space contain all possible configurations of agents which are composed of free space $\mathcal{C}_{free}$ and obstacle space $\mathcal{C}_{obs}$, where $\mathcal{C}=\mathcal{C}_{free}\cup\mathcal{C}_{obs}$ and $\mathcal{C}_{free}\cap\mathcal{C}_{obs}=\emptyset$. For a simpler explanation of how the URTS works, the following assumption is made.
\begin{assumption}
    The locating ability of the URTS is perfect so every agent can know its current configuration $q_{start}$.
\end{assumption}
\begin{assumption}
    A Task Allocation algorithm is already designed so that every agent can know its goal configuration $q_{goal}$.
\end{assumption}
\begin{assumption}
    The URTS is supposed to have a perfect real-time mapping ability so a real-time configuration space $\mathcal{C}$ can be obtained.
\end{assumption}
\begin{assumption} \label{asm:collision} % UAV do not consider obstacle collisions a little wierd.
    UAVs do not consider obstacle collisions because there are few obstacles in the air. Hence, the path of UAVs can be directly assigned rather than found by planner. Robots do not consider obstacle collisions in the direction perpendicular to the ground. 
\end{assumption}
From above assumptions, a path of agent can be expressed as a sequence
\begin{equation}
    (\sigma_n), n\in\mathbb{Z}\cap[1,k_f], \sigma_n\in\mathcal{C}
\end{equation}
where $k_f$ is the time step when reaching goal. Since the path planning is dynamic, $(\sigma_n)$ is composed of multiple segments actually. Let $(\sigma_{k_n})$ be the subsequence of $(\sigma_n)$, where $k_n$ is the time step when a replanning decision is occured. Then, the segments of path from the result of the replanning in time step $k_n$ can be expressed as sequences $(\sigma_m), m\in\mathbb{Z}\cap[k_n, k_{n+1})$. For agents, the replanning decision can be a goal changing that is made by human or Task Allocation. For robot, it can be a collision detecting by a dynamic roadmap-based planner. The results path $(\sigma_n)$ is passed to the next block, Behavior Layer.

\subsection{Behavior Layer}
% Since UAVs and robots are real physical systems, they must interact with the environment through a behavior so that they can move and act in the physical world.
Path Planning tells agents where to go but not how. Take robot as an example, it may walk, run, climb, or jump to follow the path $(\sigma_n)$ in real scenario. These behaviors with changing position are called "moving" in this paper. Besides, the agents do not always moving. Somtimes they have to suspend to take an action (e.g., getting and putting supplies, rotating in place to collect more environment information) or deal with some unexpected situations (e.g., no path found, the robot falls). These behaviors without changing position are called an "action" in this paper. More behaviors can be added so that the agent can have more ways to act with environment but there must have a corresponding behavior every moment otherwise the agent will lose control. The sequence of these behaviors be expressed as:
\begin{equation}
    (\beta_n), n\in\mathbb{Z}\cap[1,k_f], \beta_n\in\mathcal{B}
\end{equation}
It is to say that the path $(\sigma_n)$ is divided into many segments and each corresponding to a specific behavior. Judging an appropriate behavior according to the current environment will be a rather complicated project, so this article only gives the structure of the behavior set. The set of behavior $\mathcal{B}$ of agent in URTS can be roughly discribed in Fig. \ref{fig:behavior}.

@@

Now, suppose the UAV flying is occured between time step $t_1$ and $t_2$, that is, $\beta_n={flying}, n\in\mathbb{Z}\cap[t_1,t_2]$. The corresponding path $(\sigma_n), n\in\mathbb{Z}\cap[t_1,t_2]$ will be smoothed first by linear interpolation and then by cubic spline interpolation, which gives the smoothed path $(\sigma_n'), n\in\mathbb{Z}\cap[t_1,t_1+D(t_2-t_1)], \sigma_n'\in\mathbb{R}^3$, where $D\in\mathbb{Z}^+$ is the interpolation density. Then, $(\sigma_n')$ will be the position reference path $\begin{bmatrix}
    x_r[k] & y_r[k] & z_r[k]
\end{bmatrix}^T$. Subsequently, the orientation reference path, row angle $\phi_r[k]$, pitch angle $\theta_r[k]$ and yaw angle $\psi_r[k]$ are considered. $\phi_r[k]$ is set to zero since no need for spinning when flying. $\theta_r[k]$ and $\psi_r[k]$ cannot be set beforehand since UAV is an underactuated system, which will be discussed in the next section. Finally, the reference path $r[k]$ of UAV can be obtained by combining them together, i.e., $r[k] = \begin{bmatrix}
    x_r[k] & y_r[k] & z_r[k] & \psi_r[k]
\end{bmatrix}^T$. The flowchart is shown in Fig. \ref{fig:FandW}.

@@

\textit{Step 2:} Substituting $P_1=W^{-1}$ and $K=Y_1W_1^{-1}$ found in \textit{Step 1} into (\ref{eq:M}) and applying Lemma \ref{lemma2}, we obtain:
\begin{equation} \label{eq:step2}
    \begin{bmatrix}
        M_{11} & -P_1\bar{B}K - K^TRK & P_2 \\
        * & Q_2+Sym(P_2\bar{A}+Y_2\bar{C}) + K^TRK & 0 \\
        * & * & -\rho^2I
    \end{bmatrix} < 0
\end{equation}
where $Y_2=P_2L$. By solving the LMI (\ref{eq:step2}), we can obtain $P_2,Y_2$.

@@

In this case, the calculation speed of finding gains $K,L$ can be improved since the dimensionality is decrease. Furthermore, the online calculation speed of controller and observer can be also improved since there are more zeros in the gains $K,L$ found by this method while maintaining robustness. More clearly, the number of elements in matrix $K$, i.e., the number of scalar gains, changes from $n\times(sn)$ to $(1\times s)n$. For $L$, it changes from $(sn)\times(l_0n)$ to $(s\times l_0)n$.
% \textit{
%     \begin{remark}
%         This method can regard as designing the control and observer gain to each state variable, which is a common control method in practice. However, the gains are not directly adjusted but indirectly designed through prescribed specifications (\ref{Hinf}). Besides, $K_i, i=1,2,\dots,n$ do not have to be the same value (so do $L_i, i=1,2,\dots,n$). Dependent on the actual system situation, the appropriate $L_i$ and $K_i$ can be designed for each state variable by adjusting the weighting matrix $Q_i,R_i$ and attenuation level $\rho_i$ for each subsystem.
%     \end{remark}
% }

@@

\section{simulation results}
In this section, a specific S\&R procedure for URTS is given to illustrate the proposed UTRS system architecture and demonstrate the effectiveness of motion planning and control strategy. First, a S\&R area divided into $N_T$ areas, $area_j,j=1,2,...,N$, is given as shown in Fig. \ref{fig:SR_area}. To simplify the description, we will focus on the UAV and robot in $1$st team. Suppose each team has 5 agents, i.e., $N_A=5$, then we can denote $1$st team as a set, $team_1=\{ \alpha_{1,j} | j=1,2,...,5 \}$. At the beginning, the agents in $team_1$ are assigned the search tasks of $area_1$. The search task is obtained by dividing the unsearched region as shown in Fig. \ref{fig:S_task}. Representing the search tasks as a set, $task_1=\{ T_j | j=1,2,...,5 \}$, then the proper task-agent pairs can be obtained through the task allocation block, $allocation_1=\{ (\alpha_{1,j},T_j) | j=1,2,...,5 \}$. Suppose a target is found after a while as shown in Fig. \ref{fig:S_task}, at this point, we have a rescue task $T_6$. The new task list $task_2=task_1\cup\{ T_6 \}$ is obtained by updating the old one. If the ground station assigns $\alpha_{1,2}$ and $\alpha_{1,3}$ to perform $T_6$ through the task allocation algorithm, then we have the new allocation $allocation_2=(allocation_1-\{ (\alpha_{1,2},T_2),(\alpha_{1,3},T_3) \})\cup\{ \alpha_{1,2},T_6),(\alpha_{1,3},T_6) \}$. Until the S\&R mission is over, the task allocation block will continuously work in the similar way.
\begin{figure}[htbp]
    \centering
    \includegraphics[scale=.42]{fig/1.pdf}\caption{An example of a S\&R area in URTS. This area is divided into $N_T$ areas, and $j$th team is responsible for $j$th area, $area_j$}%
    \label{fig:SR_area}
\end{figure}
\begin{figure}[htbp]
    \centering
    \includegraphics[scale=.42]{fig/1.pdf}\caption{The search tasks in $1$st team at the begining. The search tasks $T_j,j=1,2,...,5$ are to reach a destinition $q_{goal}$ as shown in figure. For robots, $q_{goal}$ will be passed to path planning algorithm to find a collision path. For UAV, the path is directly assigned due to the no-collision assumption as shown in figure.}%
    \label{fig:S_task}
\end{figure}

To explain the path planning block and behavior layer block, we choose the pair $(\alpha_{1,2},T_6)$ as an example, i.e., the robot $\alpha_{1,2}$ performing the task $T_6$. From $T_6$, we have the goal configuration $q_{goal}$. With the current configuration $q_{start}$ and configuration space obtained by SLAM, the path $(\sigma_n)$ can be found as shown in Fig. \ref{fig:R_task}. The behavior sequence $(\beta_n)$ is set as shown in Fig. \ref{fig:R_task}. We choose the first walking behavior to illustrate the local motion planning block of robots. For the the UAV $\alpha_{1,1}$, the path $(\sigma_n)$ is directly set to $([ 0,0,0 ]^T, [0,0,0]^T, ...)$ without going through path planning. The behavior sequence $(\beta_n)$ of the UAV $\alpha_{1,1}$ is set to flying behavior from start to finish, i.e., $\beta_n={flying}, n\in\mathbb{Z}\cap[1,k_f]$.
\begin{figure}[htbp]
    \centering
    \includegraphics[scale=.42]{fig/1.pdf}\caption{The path planning tasks.}%
    \label{fig:R_task}
\end{figure}

Following the procedure in Fig. \ref{fig:FandW}, the resuls of local motion planning of UAV flying and robot walking are shown in Fig. \ref{fig:sim:FandW}.
\begin{figure}[htbp]
    \centering
    \includegraphics[scale=.42]{fig/1.pdf}\caption{The resuls of local motion planning of flying and walking.}%
    \label{fig:sim:FandW}
\end{figure}

@@

\textit{agents:}\begin{enumerate}
    \item system parameters: $C_0 = I_3$, $B_{2,0} = [0, 0.1, 1]^T$.
    \item designed parameters: $Q_1 = 50*diag(diag(1,100,10),$\\$ 0, 0), Q_2 = 5*diag(diag([1,100,10]), diag(1,0.1,$\\$0.01), diag(1,0.1,0.01 ,0.001)), R=0.002, \rho=30$. Actuator and sensor smoothing signal model window sizes are $3$ and $4$, respectively.
\end{enumerate}

@@

\textit{robot:}
The trajectories of reference, state and estimated state are shown in Fig. \ref{fig:robot, state}. The estimation of actuator fault $f_1(t)$ is shown in Fig. \ref{fig:robot, fa} where the distubance $d_1(t)$ in $f_1(t)$ is set as $d_1(t)=\sin(3t)$. The estimation of sensor fault $f_2(t)$ is shown in Fig. \ref{fig:robot, fs} where $f_2(t)$ is set as a smoothed square wave as shown in figure. The control effort is shown in Fig. \ref{fig:robot, control}
\begin{figure}[htbp]
    \centering
    \includegraphics[scale=.42]{fig/1.pdf}\caption{The trajectories of reference, state and estimated state of the robot $\alpha_{1,2}$}%
    \label{fig:robot, state}
\end{figure}
\begin{figure}[htbp]
    \centering
    \includegraphics[scale=.42]{fig/1.pdf}\caption{The tracking error of UAV flying.}%
    \label{fig:robot, fa}
\end{figure}
\begin{figure}[htbp]
    \centering
    \includegraphics[scale=.42]{fig/1.pdf}\caption{The tracking error of UAV flying.}%
    \label{fig:robot, fs}
\end{figure}
\begin{figure}[htbp]
    \centering
    \includegraphics[scale=.42]{fig/1.pdf}\caption{The tracking error of UAV flying.}%
    \label{fig:robot, control}
\end{figure}

>>>>

\documentclass{ieeeaccess}
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{breqn}
\usepackage{mathtools}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{float}
\usepackage[flushleft]{threeparttable}
\usepackage{bm}
\usepackage[inline]{enumitem}

% \usepackage{amsmath}
% \usepackage{amsfonts}
% \usepackage{amssymb}
% \usepackage{fontspec}
% \setmainfont{TeX Gyre Termes}

\setcounter{MaxMatrixCols}{30}
\providecommand{\U}[1]{\protect\rule{.1in}{.1in}}
\newtheorem{theorem}{Theorem}
\newtheorem{acknowledgement}[theorem]{Acknowledgement}
\newtheorem{algorithm}[theorem]{Algorithm}
% \newtheorem{axiom}[theorem]{Axiom}
\newtheorem{case}[theorem]{Case}
% \newtheorem{claim}[theorem]{Claim}
\newtheorem{conclusion}[theorem]{Conclusion}
% \newtheorem{condition}[theorem]{Condition}
% \newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{corollary}[theorem]{Corollary}
% \newtheorem{criterion}[theorem]{Criterion}
\newtheorem{definition}[theorem]{Definition}
% \newtheorem{example}[theorem]{Example}
% \newtheorem{exercise}[theorem]{Exercise}
\newtheorem{lemma}{Lemma}
\newtheorem{notation}{Notation}
\newtheorem{problem}[theorem]{Problem}
% \newtheorem{proposition}[theorem]{Proposition}
\newtheorem{remark}{Remark}
\newtheorem{solution}[theorem]{Solution}
% \newtheorem{summary}[theorem]{Summary}
\newtheorem{assumption}{Assumption}[section]
\newtheorem{ramark}{Remark}[section]
\newenvironment{proof}[1][Proof]{\noindent\textbf{#1.} }{\ \rule{0.5em}{0.5em}}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

@@

\subsection{Task Allocation}
In the URTS, it can be expected that each agent $\alpha_{i,j}$ will be assigned several specific tasks, such as searching a specific area, or delivering supplies to disaster area, etc. However, the number of agents and tasks is more than one, and each agent has different capabilities (e.g. moving speed or load capacity) and status (e.g. their own position or the amount of supplies carried), and each task has different characteristics (e.g. Urgency, position, amout of supplies needed). Therefore, the results of task allocation can be "good or bad", which leads us want to find the optimal allocation. This problem is refered as a task allocation problem or multi-robot task allocation problem. A problem formulation and a mathematical model of problem can be found in \cite{Khamis2015}. Although there are many different formulations and models to solve the task allocation problem, the common goal is to find a set of agent-task pairs to achieve a specific cost function. In this paper, we assume that the tasks have been properly assigned so that every agent knows a destinition $q_{goal}$ it needs to go at every moment.
% $(\mathcal{G})_n, n\in\mathbb{Z}\cap[1, N], N\in\mathbb{Z}^+$
\textit{
    \begin{remark}
        This block is like a commander since it is used to assign task for agents. Thus, if the real S\&R system has human experts as commanders, he can replace its job or make decisions together with it to maximize the rescue value.
    \end{remark}
}
\textit{
    \begin{remark}
        Although each agent has its own team, agents can also work across teams. For example, if the result given by the task allocation algorithm contains the agent-task pairs $(\alpha_{4,1},T_1)$ and $(\alpha_{2,2},T_1)$, then the agent $\alpha_{4,1}$ in team 1 and the agent $\alpha_{2,2}$ in team 2 will execute task $T_1$ together. 
    \end{remark}
}

\subsection{Path Planning}
After a destinition $q_{goal}$ is assigned for each agent, next step is to find a collision-free path from current position to it. There must exist multiple feasible paths to go. Similar to task allocation, we usually want to find an optimal path. There are several path planning algorithm to handle this problem. Due to the developmental and universal nature of roadmap-based path planning algorithm, this paper considers it as the path planning method of UTRS. This method attempts to discretize the search space into interconnected roads and find the path on it. 
% According to the roadmap construction method, it can be divided into deterministic and sample-based.

@@

By treating a roadmap-based path planning algorithm as a black box, the output is a sequence (or sayed waypoints), and the three inputs are current configuration $q_{start}$, goal configuration $q_{goal}$, and configuration space $\mathcal{C}$. Current configuration is obtained by GPS, inertial measurement unit, or other locating techniques. Goal configuration is obtained by the previous block, Task Allocation. Configuration space $\mathcal{C}$ is constructed by environment information through sensors of agents online or in advance by human knowledge offline. $\mathcal{C}$ is a space contain all possible configurations of agents which are composed of free space $\mathcal{C}_{free}$ and obstacle space $\mathcal{C}_{obs}$, where $\mathcal{C}=\mathcal{C}_{free}\cup\mathcal{C}_{obs}$ and $\mathcal{C}_{free}\cap\mathcal{C}_{obs}=\emptyset$. For a simpler explanation of how the URTS works, the following assumption is made.

\begin{assumption}
    The locating ability of the URTS is perfect so every agent can know its current configuration $q_{start}$.
\end{assumption}
\begin{assumption}
    A Task Allocation algorithm is already designed so that every agent can know its goal configuration $q_{goal}$.
\end{assumption}
\begin{assumption}
    The URTS is supposed to have a perfect real-time mapping ability so a real-time configuration space $\mathcal{C}$ can be obtained.
\end{assumption}
\begin{assumption} \label{asm:collision} % UAV do not consider obstacle collisions a little wierd.
    UAVs do not consider obstacle collisions because there are few obstacles in the air. Hence, the path of UAVs can be directly assigned rather than found by planner. Robots do not consider obstacle collisions in the direction perpendicular to the ground. 
\end{assumption}

From above assumptions, a path of agent can be expressed as a sequence
\begin{equation}
    (\sigma_n), n\in\mathbb{Z}\cap[1,k_f], \sigma_n\in\mathcal{C}
\end{equation}
where $k_f$ is the time step when reaching goal. Since the path planning is dynamic, $(\sigma_n)$ is composed of multiple segments actually. Let $(\sigma_{k_n})$ be the subsequence of $(\sigma_n)$, where $k_n$ is the time step when a replanning decision is occured. Then, the segments of path from the result of the replanning in time step $k_n$ can be expressed as sequences $(\sigma_m), m\in\mathbb{Z}\cap[k_n, k_{n+1})$. For agents, the replanning decision can be a goal changing that is made by human or Task Allocation. For robot, it can be a collision detecting by a dynamic roadmap-based planner. The results path $(\sigma_n)$ is passed to the next block, Behavior Layer.

\subsection{Behavior Layer}
% Since UAVs and robots are real physical systems, they must interact with the environment through a behavior so that they can move and act in the physical world.
Path Planning tells agents where to go but not how. Take robot as an example, it may walk, run, climb, or jump to follow the path $(\sigma_n)$ in real scenario. These behaviors with changing position are classified as "moving" behavior in this paper. Besides, the agents do not always moving. Somtimes they have to suspend to take an action (e.g., getting and putting supplies, rotating in place to collect more environment information) or deal with some unexpected situations (e.g., no path found, the robot falls). These behaviors without changing position are classified as "action" behavior in this paper. More behaviors can be added so that the agent can have more ways to act with environment but there must have a corresponding behavior every moment otherwise the agent will lose control. The sequence of these behaviors be expressed as:
\begin{equation}
    (\beta_n), n\in\mathbb{Z}\cap[1,k_f], \beta_n\in\mathcal{B}
\end{equation}
It is to say that the path $(\sigma_n)$ is divided into many segments and each corresponding to a specific behavior. Judging an appropriate behavior according to the current environment will be a rather complicated project, so this article only gives the structure of the behavior set. The set of behavior $\mathcal{B}$ of agent in URTS can be roughly discribed in Fig. \ref{fig:behavior}.

@@

Now, suppose the UAV flying is occured between time step $t_1$ and $t_2$, that is, $\beta_n=\mathit{flying}, n\in\mathbb{Z}\cap[t_1,t_2]$. The corresponding path $(\sigma_n), n\in\mathbb{Z}\cap[t_1,t_2]$ will be smoothed first by linear interpolation and then by cubic spline interpolation, which gives the smoothed path $(\sigma_n'), n\in\mathbb{Z}\cap[t_1,t_1+D(t_2-t_1)], \sigma_n'\in\mathbb{R}^3$, where $D\in\mathbb{Z}^+$ is the interpolation density. Then, $(\sigma_n')$ will be the position reference path $\begin{bmatrix}
    x_r[k] & y_r[k] & z_r[k]
\end{bmatrix}^T$. Subsequently, the orientation reference path, row angle $\phi_r[k]$, pitch angle $\theta_r[k]$ and yaw angle $\psi_r[k]$ are considered. $\phi_r[k]$ is set to zero since no need for spinning when flying. $\theta_r[k]$ and $\psi_r[k]$ cannot be set beforehand since UAV is an underactuated system, which will be discussed in the next section. Finally, the reference path $r[k]$ of UAV can be obtained by combining them together, i.e., $r[k] = \begin{bmatrix}
    x_r[k] & y_r[k] & z_r[k] & \psi_r[k]
\end{bmatrix}^T$. The flowchart is shown in Fig. \ref{fig:FandW}.

@@

\textit{Step 2:} Substituting $P_1=W_1^{-1}$ and $K=Y_1W_1^{-1}$ found in \textit{Step 1} into (\ref{eq:M}) and applying Lemma \ref{lemma2}, we obtain:
\begin{equation} \label{eq:step2}
    \begin{bmatrix}
        M_{11} & -P_1\bar{B}K - K^TRK & P_2 \\
        * & Q_2+Sym(P_2\bar{A}+Y_2\bar{C}) + K^TRK & 0 \\
        * & * & -\rho^2I
    \end{bmatrix} < 0
\end{equation}
where $Y_2=P_2L$. By solving the LMI (\ref{eq:step2}), we can obtain $P_2,Y_2$.

@@

In this case, the calculation speed of finding gains $K,L$ can be improved since the dimensionality is decrease. Furthermore, the online calculation speed of controller and observer can be also improved since there are more zeros in the gains $K,L$ found by this method while maintaining robustness. More clearly, the number of elements in matrix $K$, i.e., the number of scalar gains, changes from $n\times(sn)$ to $(1\times s)\times n$. For $L$, it changes from $(sn)\times(l_0n)$ to $(s\times l_0)\times n$.
% \textit{
%     \begin{remark}
%         This method can regard as designing the control and observer gain to each state variable, which is a common control method in practice. However, the gains are not directly adjusted but indirectly designed through prescribed specifications (\ref{Hinf}). Besides, $K_i, i=1,2,\dots,n$ do not have to be the same value (so do $L_i, i=1,2,\dots,n$). Dependent on the actual system situation, the appropriate $L_i$ and $K_i$ can be designed for each state variable by adjusting the weighting matrix $Q_i,R_i$ and attenuation level $\rho_i$ for each subsystem.
%     \end{remark}
% }

@@

\section{simulation results}
In this section, a specific S\&R procedure for URTS is given to illustrate the proposed UTRS system architecture and demonstrate the effectiveness of motion planning and control strategy. First, a S\&R area divided into $N_T$ areas, $area_j,j=1,2,...,N$, is given as shown in Fig. \ref{fig:SR_area}. To simplify the description, we will focus on the UAV and robot in $1$st team. Suppose each team has 5 agents, i.e., $N_A=5$, then we can denote $1$st team as a set, $team_1=\{ \alpha_{1,j} | j=1,2,...,5 \}$. At the beginning, the agents in $team_1$ are assigned the search tasks of $area_1$ to build the occupy map and find targets. The search task is assumed to be obtained by dividing the unsearched region as shown in Fig. \ref{fig:S_task}. Representing the search tasks as a set, $task_1=\{ T_j | j=1,2,...,5 \}$, then the proper agent-task pairs can be obtained through the task allocation block, $allocation_1=\{ (\alpha_{1,j},T_j) | j=1,2,...,5 \}$. Suppose a target is found after a while as shown in Fig. \ref{fig:S_task}, at this point, we have a rescue task $T_6$. The new task list $task_2=task_1\cup\{ T_6 \}$ is obtained by updating the old one. If the ground station assigns $\alpha_{1,2}$ and $\alpha_{1,3}$ to perform $T_6$ through the task allocation algorithm, then we have the new allocation $allocation_2=(allocation_1-\{ (\alpha_{1,2},T_2),(\alpha_{1,3},T_3) \})\cup\{ \alpha_{1,2},T_6),(\alpha_{1,3},T_6) \}$. Until the S\&R mission is over, the task allocation block will continuously work in the similar way.
\begin{figure}[htbp]
    \centering
    \includegraphics[scale=.42]{fig/1.pdf}\caption{An example of a S\&R area in URTS. This area is divided into $N_T$ areas, and $j$th team is responsible for $j$th area, $area_j$}%
    \label{fig:SR_area}
\end{figure}
\begin{figure}[htbp]
    \centering
    \includegraphics[scale=.42]{fig/1.pdf}\caption{The search tasks in $1$st team at the begining. The search tasks $T_j,j=1,2,...,5$ are to reach a destinition $q_{goal}$ as shown in figure. For robots, $q_{goal}$ will be passed to path planning algorithm to find a collision path. For UAV, the path is directly assigned due to the no-collision assumption as shown in figure.}%
    \label{fig:S_task}
\end{figure}

To explain the path planning block and behavior layer block, we choose the pair $(\alpha_{1,2},T_6)$ as an example, i.e., the robot $\alpha_{1,2}$ performing the task $T_6$. From $T_6$, we have the goal configuration $q_{goal}$. With the current configuration $q_{start}$ and configuration space obtained by SLAM, the path $(\sigma_n),n\in\mathbb{Z}\cap[1,k_f],k_f=27$ can be found as shown in Fig. \ref{fig:R_task}. The behavior sequence $(\beta_n)$ is set as $\beta_n=\mathit{walking},n\in\mathbb{Z}\cap[1,5]$, $\beta_n=\mathit{climbing},n\in\mathbb{Z}\cap[6,15]$, $\beta_n=\mathit{running},n\in\mathbb{Z}\cap[16,27]$. We choose the first walking behavior to illustrate the local motion planning block of robots.

For the the UAV $\alpha_{1,1}$, the path $(\sigma_n),n\in\mathbb{Z}\cap[1,k_f],k_f=9$ is directly set to $([0,0,0]^T\mathbin{,} [0,5,2.5]^T\mathbin{,} [5,5,5]^T\mathbin{,} [5,0,2.5]^T\mathbin{,} [10,0,0]^T\mathbin{,} [10,5,-2.5]^T\mathbin{,} [10,10,-5]^T\mathbin{,} [5,10,-2.5]^T\mathbin{,} [0,10,0]^T)$ without going through path planning by \textit{Assumption \ref{asm:collision}}. The behavior sequence $(\beta_n)$ is set as $\beta_n=\mathit{flying}, n\in\mathbb{Z}\cap[1,9]$.
\begin{figure}[htbp]
    \centering
    \includegraphics[scale=.42]{fig/1.pdf}\caption{The path planning tasks.}%
    \label{fig:R_task}
\end{figure}

Following the procedure in Fig. \ref{fig:FandW}, the results of local motion planning of UAV flying and robot walking are shown in Fig. \ref{sim:flying} and \ref{sim:walking}.
\begin{figure}[htbp]
    \centering
    \includegraphics[scale=.42]{fig/1.pdf}\caption{The top view of result of local motion planning of flying.}%
    \label{sim:flying}
\end{figure}
\begin{figure}[htbp]
    \centering
    \includegraphics[scale=.42]{fig/untitled.png}\caption{The top view of result of local motion planning of walking.}%
    \label{sim:walking}
\end{figure}

@@

\textit{agents:}\begin{enumerate}
    \item system parameters: $C_0 = I_3$, $B_{2,0} = [0, 0.1, 1]^T$.
    \item designed parameters: $Q_1 = 50*diag(diag(1,100,10),\allowbreak 0, 0), Q_2 = 5*diag(diag([1,100,10]), diag(1,0.1,\allowbreak 0.01), diag(1,0.1,0.01 ,0.001)), R=0.002, \rho=30$. Actuator and sensor smoothing signal model window sizes are $3$ and $4$, respectively.
\end{enumerate}

@@

\textit{robot:}
The trajectories of reference, state and estimated state are shown in Fig. \ref{fig:robot, state}. The estimation of actuator fault $f_1(t)$ is shown in Fig. \ref{fig:robot, fa} where the distubance $d_1(t)$ in $f_1(t)$ is set as $d_1(t)=\sin(3t)$. The estimation of sensor fault $f_2(t)$ is shown in Fig. \ref{fig:robot, fs} where $f_2(t)$ is set as a smoothed square wave as shown in figure. The control effort is shown in Fig. \ref{fig:robot, control}
\begin{figure}[htbp]
    \centering
    \includegraphics[scale=.42]{fig/1.pdf}\caption{The trajectories of reference, state and estimated state of the robot $\alpha_{1,2}$}%
    \label{fig:robot, state}
\end{figure}
\begin{figure}[htbp]
    \centering
    \includegraphics[scale=.42]{fig/1.pdf}\caption{The estimation of actuator fault of the robot $\alpha_{1,2}$.}%
    \label{fig:robot, fa}
\end{figure}
\begin{figure}[htbp]
    \centering
    \includegraphics[scale=.42]{fig/1.pdf}\caption{The estimation of sensor fault of the robot $\alpha_{1,2}$}%
    \label{fig:robot, fs}
\end{figure}
\begin{figure}[htbp]
    \centering
    \includegraphics[scale=.42]{fig/1.pdf}\caption{The control effort of the robot $\alpha_{1,2}$}%
    \label{fig:robot, control}
\end{figure}

In Fig. \ref{fig:UAV, state} and Fig. \ref{fig:robot, state}, the tracking and estimation errors have reached a steady state at x seconds. The transient responses that occur later are caused from fault signals, especially the sensor fault. This can be inferred from the dynamic of the estimation error (\ref{eq:e_tilde}) because the value of the sensor fault affects the value of the estimation error over time $\dot{e}$ not only from the term $\bar{A}$ but also from the term $L\bar{C}$. In Fig \ref{fig:UAV, fa} and \ref{fig:robot, fa}, the results show that the actuator fault, i.e., disturbance and feedforward errors, can be effectively estimated. In Fig \ref{fig:UAV, fs} and \ref{fig:robot, fs}, the estimation of sensor fault has an overshot phenomenon when there is a large change, but returns to a steady state after about $3$ seconds. In Fig \ref{fig:UAV, control} and \ref{fig:robot, control}, the control effort has high frequency and high amplitude performance at the initial instance due to the high gain characteristic of the robust control, and then maintains the sine wave shape to offset the estimated actuator fault value.
